Probability

### 2016-04-30 prob.tex
prob.tex \paragraph*{Interval-valued probability measures.} update...

\newpage

\[\begin{array}{rclrcll}
\imposs \vee x &=& x \vee \imposs &=& x \\
\necess \vee x &=& x \vee \necess  &=& \necess \\
\unlikely \vee \likely &=& \likely \vee \unlikely &=& \necess
\end{array}\]

If we consider set
with more values, the probability measure may give us more information
about the coins. For example, despite $\imposs$ and $\poss$, we may
also adopt three more values: $\unlikely$\ as the
interval~$\left(0,\frac{1}{2}\right]$, $\likely$\ as the
interval~$\left(\frac{1}{2},1\right]$, and $\overflow$\ as the empty
set~$\emptyset$ which means the total probability may be excessed than
one. In particular, $\likely\vee\likely=\overflow$ because the
probability of two disjoint events should not both bigger than
$\frac{1}{2}$. The complete rule for operator~$\vee$ on
$\mathscr{L}_{5}=\left\{
  \imposs,\poss,\unlikely,\likely,\overflow\right\} $
is defined in table~\ref{tab:The-operator-on}, or more abstractly, we
define $(a,b]\vee(c,d]=(a+c,b+d]\cap[0,1]$. The definition of a
probability measure can be modified as a function
$\pmeas:\events\rightarrow\mathscr{L}_{5}$ such that:
\begin{itemize}
\item $\pmeas(\Omega)\in\left\{ \poss,\likely\right\} $ or equivalently
$1\in\pmeas(\Omega)$, and 
\item for a collection $E_{i}$, of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_{i}\pmeas(E_{i})$. 
\end{itemize}
\begin{table}
\center{%
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
$\vee$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
\hline 
\hline 
$\imposs$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
\hline 
$\poss$ & $\poss$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
\hline 
$\unlikely$ & $\unlikely$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
\hline 
$\likely$ & $\likely$ & $\likely$ & $\likely$ & $\overflow$ & $\overflow$\tabularnewline
\hline 
$\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$\tabularnewline
\hline 
\end{tabular}}

\caption{\label{tab:The-operator-on}The operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $}
\end{table}

>>>>

In interval-valued probability measures, if $\mu\left(E\right)=\left[a,b\right]$,
the left-endpoint~$a$ called belief denotes the strength of the
evidence that $E$ happens, and the right-endpoint~$b$ called plausibility
denotes the strength of the evidence that contradicts $E$. If we
define $1-\left[a,b\right]=\left[1-b,1-a\right]$, then we intuitively
have 
\begin{eqnarray*}
\pmeas\left(\emptyset\right) & = & \imposs\\
\pmeas\left(\Omega\right) & = & \necess\\
\pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
\end{eqnarray*}
Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
then 
\begin{itemize}
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
\end{itemize}
Notice that the equality may not hold in general This statement says
that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
putting all the evidences of $E_{i}$ together, but some evidence
may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
$\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
but may not equal. In our example, 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
 & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
\end{eqnarray*}
However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
because if we check the complement of $\{HH,TH\}$, we have 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
\end{eqnarray*}
and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
of $\{HH\}$ and $\{TH\}$ individually.

\yutsung{Although this is clearer than the previous one, I keep some
intervals instead write everything in \imposs, \unlikely, \likely,
and \necess. The biggest point is the addition rule~$\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$:
\begin{itemize}
\item This rule without \overflow will be push complexity to ``we may abort
computing probability when....''
\item It seems more concisely than a table among \imposs, \unlikely, \likely,
and \necess.
\end{itemize}
However, if you prefer as less interval as possible, I may try to
replace them by \imposs, \unlikely, \likely, and \necess...}
